The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-08-17 paper.tex
give the antenna beam figure the same treatment as the psf figure

\begin{figure*}[t]
    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
    \caption{
        (left panel) The tracks traced through the sky by the 8 brightest point sources visible to the
        OVRO-LWA.
        (right panel) The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
    }
    \label{fig:beam}
\end{figure*}

>>>>

\begin{figure*}[t]
    \includegraphics[width=\textwidth]{figures/beam/beam}
    \caption{
        \textbf{(left panel)}
        The tracks traced through the sky by the 8 brightest point sources visible to the
        OVRO-LWA.
        \textbf{(middle panel)}
        The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
        \textbf{(right panel)}
        The amplitude of the OVRO-LWA beam at 73.152 MHz as a result of the beam model
        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
    }
    \label{fig:beam}
\end{figure*}
